---
title: "up_down_vis"
author: "Maggie Schedl"
date: "3/31/2020"
output: html_document
---



should split up original ven diagram by up and down regulated 

visualizing up and down regulated 

CA # 142 up, 349 down
SE # 142 up, 237 down
CASE # 162 up, 433 down

How do I separate out who those are? hmm maybe LF change is neg
in my ordered list 

```{r}
getwd()
```


running from DESeq R script for the results files actually, these I want because I can do the subset function on them on the log2fold change value
```{r}
sig_CA <- subset(results_CA_F, padj<0.05) #identify signficant pvalues with 5%FDR 
sig_SE <- subset(results_SE_F, padj<0.05)
sig_CASE <- subset(results_CASE_F, padj<0.05)

# These are formal class DESeq resuts which I want

Up_Sig_SE <- subset(sig_SE, log2FoldChange>0) # greater than 0
Down_Sig_SE <- subset(sig_SE, log2FoldChange<0) # less than 0
Up_Sig_CA <- subset(sig_CA, log2FoldChange>0)
Down_Sig_CA <- subset(sig_CA, log2FoldChange<0)
Up_Sig_CASE <- subset(sig_CASE, log2FoldChange>0)
Down_Sig_CASE <- subset(sig_CASE, log2FoldChange<0)


write.table(Up_Sig_SE,"Up_Sig_SE.txt",quote=FALSE,col.names=TRUE,row.names=TRUE,sep="\t")
write.table(Down_Sig_SE,"Down_Sig_SE.txt",quote=FALSE,col.names=TRUE,row.names=TRUE,sep="\t")
write.table(Up_Sig_CA,"Up_Sig_CA.txt",quote=FALSE,col.names=TRUE,row.names=TRUE,sep="\t")
write.table(Down_Sig_CA ,"Down_Sig_CA.txt",quote=FALSE,col.names=TRUE,row.names=TRUE,sep="\t")
write.table(Up_Sig_CASE,"Up_Sig_CASE.txt",quote=FALSE,col.names=TRUE,row.names=TRUE,sep="\t")
write.table(Down_Sig_CASE,"Down_Sig_CASE.txt",quote=FALSE,col.names=TRUE,row.names=TRUE,sep="\t")
```


Then work on the venn diagrams

Down Regulated 
```{r}
DSE_genes <- row.names(Down_Sig_SE) #just gets the names of the genes, which is all that is needed to compare
DCA_genes <- row.names(Down_Sig_CA)
DCASE_genes <- row.names(Down_Sig_CASE)

DownRegulatedSigGenes <- c(DSE_genes, DCA_genes, DCASE_genes) #combine the list

DRSG_uniq_list <- CASE_deseq_Matrix_Factors[which(rownames(CASE_deseq_Matrix_Factors) %in% DownRegulatedSigGenes),] #gets rid of any duplicates 

#but using from the matrix, it has all the other information again we don't need
DRSG_uniq <- row.names(DRSG_uniq_list) #make just the names of the genes again

# Comparing each individual list with the combined list
# What are the ones in CA that are in the total? Gives back a list of true and falses 
DSE_genes.2 <- DRSG_uniq %in% DSE_genes
DCA_genes.2 <- DRSG_uniq %in% DCA_genes
DCASE_genes.2 <- DRSG_uniq %in% DCASE_genes


# Generating venn counts to plot venn diagram  
DRcomb <- cbind(DSE_genes.2, DCA_genes.2, DCASE_genes.2)
DRvenn <- vennCounts(DRcomb)
vennDiagram(DRvenn, cex = 1,names = c("SE", "CA", "CASE"), circle.col = c("#593959", "#2e5eaa", "#40a08e"))
```
I think these are right... 


Up Regulated 

```{r}
USE_genes <- row.names(Up_Sig_SE) #just gets the names of the genes, which is all that is needed to compare
UCA_genes <- row.names(Up_Sig_CA)
UCASE_genes <- row.names(Up_Sig_CASE)

UpRegulatedSigGenes <- c(USE_genes, UCA_genes, UCASE_genes) #combine the list

URSG_uniq_list <- CASE_deseq_Matrix_Factors[which(rownames(CASE_deseq_Matrix_Factors) %in% UpRegulatedSigGenes),] #gets rid of any duplicates 

#but using from the matrix, it has all the other information again we don't need
URSG_uniq <- row.names(URSG_uniq_list) #make just the names of the genes again
URSG_uniq
# Comparing each individual list with the combined list
# What are the ones in CA that are in the total? Gives back a list of true and falses 
USE_genes.2 <- URSG_uniq %in% USE_genes
UCA_genes.2 <- URSG_uniq %in% UCA_genes
UCASE_genes.2 <- URSG_uniq %in% UCASE_genes


# Generating venn counts to plot venn diagram  
URcomb <- cbind(USE_genes.2, UCA_genes.2, UCASE_genes.2)
URvenn <- vennCounts(URcomb)
vennDiagram(URvenn, cex = 1,names = c("SE", "CA", "CASE"), circle.col = c("#593959", "#2e5eaa", "#40a08e"))
```

probably separate lists of these overlaping ones will be helpful

Down Reg shared
```{r}
DSE_CA_Overlap <- intersect(DSE_genes, DCA_genes)
DSE_CASE_Overlap <- intersect(DSE_genes, DCASE_genes)
DCA_CASE_Overlap <- intersect(DCASE_genes, DCA_genes)
DCA_CASE_Overlap
```
209 overlap between CA and CASE, which is 165 plus 44 so the venn diagrams are correct!

Up Reg Shared
```{r}
USE_CA_Overlap <- intersect(USE_genes, UCA_genes)
USE_CASE_Overlap <- intersect(USE_genes, UCASE_genes)
UCA_CASE_Overlap <- intersect(UCASE_genes, UCA_genes)

```

