---
title: "Diff-Mod-Comp"
author: "Maggie Schedl"
date: "3/23/2020"
output: github_document
---


# Setup
```{r}
getwd()
```

```{r}
library(dplyr)
library(tidyr)
library(genefilter)

```


```{r}
#First read in the two lists
GYGenes <- read.csv("GYModGeneNames.csv")
SigSE <- read.table("ordered_sig_SE.txt")
SigCASE <- read.table("ordered_sig_CASE.txt")
```

Ok they are not in the right format yet to be made into a venn diagram. 
I need them as... lists I think
```{r}
SElist <- rownames(SigSE)
CASElist <- rownames(SigCASE)
GYgenes <- GYGenes$GYGeneNames

GYgenes
CASElist
```

```{r}
# combine the three lists together

CombSECASEGY <- c(SElist, CASElist, GYgenes) 
CombSECASEGY
#I think this removes duplicates 
UCombSECASEGY <- unique(CombSECASEGY)
UCombSECASEGY
```


```{r}
#now compare each individual list to the combined list, which is why you want the duplicates removed

# Comparing each individual list with the combined list
SE_overlap <- UCombSECASEGY %in% SElist
GY_Overlap <- UCombSECASEGY %in% GYgenes 
CASE_overlap <- UCombSECASEGY %in% GYgenes

```

```{r}
# Generating venn counts to plot venn diagram
Overlap1 <- cbind(SE_overlap, GY_Overlap, CASE_overlap)
Ven1 <- vennCounts(Overlap1)
vennDiagram(Ven1, cex = 1,names = c("SE", "GY", "CASE"), circle.col = c("#2e5eaa", "#593959", "#40a08e"))

```
I'm not sure if this is right. 

https://www.r-graph-gallery.com/14-venn-diagramm.html

https://www.data-to-viz.com/story/SeveralIndepLists.html

```{r}
library(VennDiagram)
library(scales)
```

```{r}
# Chart
venn.diagram(
  x = list(SElist, GYgenes, CASElist),
  category.names = c("SE" , "GY " , "CASE"),
   filename = 'Test-venn.png',
  output = TRUE ,
          imagetype="png" ,
          height = 480 , 
          width = 480 , 
          resolution = 300,
          compression = "lzw",
          lwd = 1,
          col=c("#440154ff", '#21908dff', '#fde725ff'),
          fill = c(alpha("#440154ff",0.3), alpha('#21908dff',0.3), alpha('#fde725ff',0.3)),
          cex = 0.5,
          fontfamily = "sans",
          cat.cex = 0.6,
          cat.default.pos = "outer",
          cat.pos = c(-27, 27, 135),
          cat.dist = c(0.055, 0.055, 0.085),
          cat.fontfamily = "sans",
          cat.col = c("#440154ff", '#21908dff', '#fde725ff'),
          rotation = 1
        )




```
This looks a little weird, it's like it's missing an overlap...

How can I see what those actual genes are?
https://www.biostars.org/p/163635/

```{r}

shared_SE_GY <- intersect(SElist, GYgenes)
shared_SE_GY

shared_CASE_GY <- intersect(CASElist, GYgenes)
shared_CASE_GY

shared_CASE_SE <- intersect(CASElist, SElist)
shared_CASE_SE

intersect <- intersect(shared_CASE_GY, shared_SE_GY)
intersect

write.table(intersect,"GYSECASEoverlap.txt",quote=FALSE,col.names=TRUE,row.names=TRUE,sep="\t")
# ok this means that there are no shared genes between SE and GY that aren't shared between CASE and GY 
```

It's only 14, should I BLAST these? ¯\_(ツ)_/¯



Can I do just 2?

```{r}
venn.diagram(
  x = list(SElist, GYgenes),
  category.names = c("SE" , "GY "),
   filename = 'SE-GY-venn.png',
  output = TRUE ,
          imagetype="png" ,
          height = 480 , 
          width = 480 , 
          resolution = 300,
          compression = "lzw",
          lwd = 1,
          col=c("#440154ff", '#21908dff'),
          fill = c(alpha("#440154ff",0.3), alpha('#21908dff',0.3)),
          cex = 0.5,
          fontfamily = "sans",
          cat.cex = 0.6,
          cat.default.pos = "outer",
          cat.pos = c(-27, 27),
          cat.dist = c(0.055, 0.055),
          cat.fontfamily = "sans",
          cat.col = c("#440154ff", '#21908dff'),
          rotation = 1
        )
```

no I cannot





Can I compare with Up regulated DEGs from SE and CASE?

```{r}

Up_Sig_SE <- read.table("Up_Sig_SE.txt")
Up_Sig_CASE <- read.table("Up_Sig_CASE.txt")
GYGenes <- read.csv("GYModGeneNames.csv")

Up_SElist <- rownames(Up_Sig_SE)
Up_CASElist <- rownames(Up_Sig_CASE)
GYgenes <- GYGenes$GYGeneNames

GYgenes

Up_SE_CASE_GY <- c(Up_SElist, Up_CASElist, GYgenes) 

#it's just the names, I can still use this method that works 
Up_SE_CASE_GY_list <- CASE_deseq_Matrix_Factors[which(rownames(CASE_deseq_Matrix_Factors) %in% Up_SE_CASE_GY),] #gets rid of any duplicates


#but using from the matrix, it has all the other information again we don't need
Up_SE_CASE_GY_uniq <- row.names(Up_SE_CASE_GY_list) #make just the names of the genes again

# Comparing each individual list with the combined list
# What are the ones in CA that are in the total? Gives back a list of true and falses 
Up_SElist.2 <- Up_SE_CASE_GY_uniq %in% Up_SElist
Up_CASElist.2 <- Up_SE_CASE_GY_uniq %in% Up_CASElist
GYgenes.2 <- Up_SE_CASE_GY_uniq %in% GYgenes

GYgenes.2

# Generating venn counts to plot venn diagram  
UP_SE_CASE_GYcomb <- cbind(Up_SElist.2, Up_CASElist.2, GYgenes.2)
D_SE_CASE_GY_venn <- vennCounts(UP_SE_CASE_GYcomb)
vennDiagram(DRvenn, cex = 1,names = c("SE", "CASE", "GY"), circle.col = c("#593959", "#2e5eaa", "#40a08e"))


```

uhhhh why is this so wrong. There are only 57 genes in the GY module?????
